\documentclass[a4paper, 12pt]{report}
\usepackage{thesis_style}	%look at the style file for packages and graphics

\begin{document}
	
	%!TeX program = lualatex

\input{header}
%\newpage\null\thispagestyle{empty}\newpage

\pagenumbering{roman}

\tableofcontents
%\thispagestyle{empty}
%\cleardoublepage

%\listoffigures

\chapter*{Abstract}
\input{chapters/abstract}

\chapter{Introduction}
\label{intro}
\pagenumbering{arabic}
\setcounter{page}{1}
\input{chapters/introduction}

\chapter{Monte Carlo simulations}  
\input{chapters/Sullivan}    
\input{chapters/MC}

\chapter{Instrumentation characterization}
\input{chapters/instrumentation_characterization}

\chapter{Lifetime measurement}
\input{chapters/lifetime_measurement}

\part*{Appendix}

\appendix

\chapter{Free muon decay}
\label{Appendix A}
\input{chapters/appendix_free_muon_decay}

\chapter{Monte Carlo simulations}
\label{Appendix B}
\input{chapters/appendix_MC_simulations}

\chapter{Technical specifications}
\input{chapters/appendix_technical_specifications}

\chapter{Collected data}
\input{chapters/appendix_data}

\chapter{DAQ software}
\input{chapters/appendix_daq}

\chapter{Background evaluation}
\input{chapters/appendix_background}

\newpage

\begin{thebibliography}{30}


\bibitem{PDG} M. Tanabashi \emph{et al}	(Particle Data Group), \emph{Phys. Rev.} D\textbf{98}, 030001 (2018), \texttt{DOI}: \href{http://pdg.lbl.gov/}{10.1103/PhysRevD.98.030001}.
%http://pdg.lbl.gov/2002/pardetrpp.pdf
%http://pdg.lbl.gov/2019/reviews/rpp2019-rev-cosmic-rays.pdf

\bibitem{Longair}
Malcom S. Longair, \emph{High Energy Astrophysics}, Cambridge University Press, Third Edition.

\bibitem{Mandl Shaw}
F. Mandl, G. Shaw, \emph{The Quantum Field Theory}, Second Edition, Wiley.

\bibitem{TRandom3}
\texttt{ROOT} Reference Documentation, \texttt{TRandom3} Class Reference, \url{https://root.cern.ch/doc/master/classTRandom3.html}.

\bibitem{MT} M. Matsumoto, T. Nishimura., \emph{Mersenne Twister: A 623-Dimensionally Equidistributed Uniform Pseudo-RandomNumber Generator}, \emph{ACM Transactions on Modeling and Computer Simulation}, Vol. 8, No. 1, pp 3-30, 1998, \texttt{DOI}: \href{https://dl.acm.org/doi/pdf/10.1145/272991.272995?download=true}{10.1145/272991.272995}.

\bibitem{Measday} D.F. Measday, \emph{The nuclear physics of muon capture}, Physics Reports 354, 243–409 (2001).

\bibitem{Knoll} Glenn F. Knoll, \emph{Radiation Detection and Measurament}, John Wiley and Sons, Fourth Edition.

\bibitem{Weissenberg} A. O. Weissenberg. \emph{Muons} North Holland Publisher.

\bibitem{sutton} R.B. Sutton et al. \emph{Measurement of negative muon lifetimes in light isotopes}.

	\bibitem{Sullivan}
	J.D. Sullivan, 
	\textit{Geometrical factor and directional response of single and multi-element particle telescopes}, 
	Nuclear Instruments and Methods, 
	Vol. 95, 
	pp. 5-11, 
	1971, 
	\texttt{DOI}: \href{https://doi.org/10.1016/0029-554X(71)90033-4}{10.1016/0029-554X(71)90033-4}, 
	\url{http://www.sciencedirect.com/science/article/pii/0029554X71900334}.
	
	\bibitem{Thomas}
	G.R. Thomas and D.M. Willis, 
	\textit{Analytical derivation of the geometric factor of a particle detector having circular or rectangular geometry}, 
	Journal of Physics E: Scientific Instruments,
	Vol. 5, 
	pp. 260-263, 
	1972, 
	\texttt{DOI}: \href{https://iopscience.iop.org/article/10.1088/0022-3735/5/3/024}{10.1088/0022-3735/5/3/024}
	\url{https://doi.org/10.1088\%2F0022-3735\%2F5\%2F3\%2F024}.
	
\bibitem{lifetime} T. Suzuki, D. F. Measday, J. P. Roalsvig, \emph{Total nuclear capure rates for negative muons}, Phys. Rev. C 35, 2212, 1987, \texttt{DOI}: \url{https://doi.org/10.1103/PhysRevC.35.2212}.

\bibitem{charge} The CMS Collaboration, \emph{Measurement of the charge ratio of atmospheric muons with the CMS detector}, Physics Letters B, 2010, arXiv: \href{https://arxiv.org/pdf/1005.5332.pdf}{1005.5332}.

\bibitem{pull} Luc Demortier, Louis Lyons,
\emph{Everything you always wanted to know about pulls} CDF/ANAL/PUBLIC/5776 Version 2.10, August 20, 2002.

\end{thebibliography}

\end{document}